#Class Exercise Using R Markdown
========================================================
###**Load the data**
First, load the necessary packages:
```{r}
require(ggplot2)
require(reshape2)
```
Then load the data from gapminder.
```{r}
gapminder <- as.data.frame(read.delim("gapminderDataFiveYear.txt"))
```

Then, evaluate the structure of _gapminder_
```{r}
str(gapminder)
```
Determine which countries are available for selection
```{r}
head(gapminder$country)

```
Select 3 countries: **Afghanistan, Australia, India***
```{r}
data <- subset(gapminder, country %in% c("Afghanistan", "Australia", "India"))
```
Output the plots
```{r}
ggplot(data, aes(year, gdpPercap, color = country))+
  geom_point()+
  facet_wrap(~ country)
```
Key Points (Based on the plots):
* Afghanistan has seen a fairly flat trend for GDP and has a considerably lower GDP than the other countries.  
* Australia is considerably more wealthy than the other countries (as evidenced by GDP) and has seen an almost exponential increase during the period of record.  
* India has considerably lower GDP, but appears to be entering a period of substantial increase.

